PInSoRo: A Dataset for Deep-Learning of Human-Robot Social Interactions

### 2017-06-28 paper.tex
Submitted version

The children's faces are recorded using two short range Intel RealSense SR300
RGB-D cameras (0.2m to 1.2m) placed at the corners of the the sandtray
(Fig.~\ref{fig|freeplay}) and tilted to face the children. The
cameras are rigidly mounted on custom 3D-printed brackets. This enables a
precise measurement of their 6D pose relative to the touchscreen (extrinsic
calibration).

@@

\newcommand{\tabitem}{~~\llap{\textbullet}~~}
    \begin{tabular}{@{}p{0.2\linewidth}p{0.8\linewidth}@{}}
\toprule
\bf Greetings                     & \tabitem explain the purpose of the study: showing robots how children play  \\
\emph{(about 5 min)}              & \tabitem briefly present a Nao robot: the robot stands up, gives a short
                                    message (\emph{"Hello, I'm Nao. Today, I'll be watching you while you
                                    play and soon I'll be able to play with you. Is that alright?"}), and
                                    sits down. The robot is then put aside and does not intervene
                                    for the remaining of the experiment \\
                                    %Condition B: "Hello, I'm Nao. Today I'll be playing with you. Exciting!")\\ 
                                  & \tabitem place children on cushions \\ 
                                  & \tabitem give them the yellow/purple sports
                                  bibs and make sure their hair is tied \\ 
                                  & \tabitem complete demographics on the tablet \\
                                  & \tabitem remind the children that they can withdraw at anytime \\ \midrule
\bf Visual focus task             & \emph{(unrelated visual task where children gaze at a moving target)}\\ 
\emph{(30 sec)}                   & \\ \midrule
\bf Tutorial                      & explain how to interact with the game, ensure the children are confident with the manipulation/drawing \\ 
\emph{(1-2 min)}                  & \\ \midrule
\bf Items placement game          & \emph{(unrelated task on spatial reasoning -- as this task uses the same graphical environment as the main free-play task, it helps the children to familiarise themselves with the game environment)} \\
\emph{(5 to 10 min)}              &  \\ \midrule
\bf Freeplay task                 & \tabitem initial prompt: \emph{"Just to remind you, you can use the animals or draw. Whatever you
                                  like. If you run out of ideas, there's also an ideas box. For example, the first one is a
                                  zoo. You could draw a zoo or tell a story. When you get bored or don't want to play
                                  anymore, just let me know."} \\
                                  & \tabitem let children play \\
                                  & \tabitem once they wish to stop, stop recording \\ \midrule
\bf Debriefing                    &  \tabitem answer possible questions from the children \\
\emph{(about 2 min)}              & \tabitem give stickers as a thank you \\ \bottomrule
\end{tabular}

@@

The last part of the dataset consist in annotations of the children's social
behaviours. These behaviours are either automatically computed and coded
(mutual gaze, for instance), or are human-coded. The annotations are all
timestamped and integrated as an independent datastream in the dataset.

@@

The dataset includes two types of manual annotations: \emph{remarkable events},
annotated by the experimenter during the experiment as free text annotation, and
\emph{social behaviours} coded with the \emph{Social Communication Coding
System} (SCCS) proposed by Olswang~\etal\cite{olswang2006reliability}.
These annotations are performed post-hoc, with a dedicated tool, able to replay synchronously
the main datastreams (Fig.~\ref{fig|analysis}).

The SCCS consists in 6 mutually exclusive constructs characterising social
communication (Table~\ref{table|sccs}). These behaviours represent a typical
classification output that a network could be trained to recognise.

@@

\begin{figure}[b!]
    \centering
    \includegraphics[width=0.8\linewidth]{analysis}
    \caption{Screenshot of our interaction annotation tool: the recorded interaction data
    is played back synchronously (faces and audio of the two children,
    interaction occurring on the interactive table, etc.) while the human coder
    annotate the record timeline with social situations of interest.}
    \label{fig|analysis}
\end{figure}

@@

The dataset is freely available to any interested researcher\footnote{Note to
the reviewers: for the purpose of the review, an excerpt of the dataset is
available online: \url{https://freeplay-sandbox.github.io/}. A link to the
complete dataset will be made available in the final version of the article.}.
Due to ethical and data protection regulations, the dataset is however made
available in two forms: a public, Creative Commons licensed, version that does
not include any video material of the children (no video streams, audio
included); and a complete version that includes all video streams. This second
version is freely available as well, but interested researchers must first fill
a data protection form.

@@

During the acquisition campaign for the PInSoRo dataset, we have also recorded a
\emph{child-robot} interaction baseline. We were using the exact same protocol
as described above, only with one child replaced by a Nao robot.

The robot was fully autonomous, and programmed to exhibit a non-social behaviour
(its action policy was simply to repeatedly move interactive items to
pre-defined zones, entirely ignoring its child partner).

As such, this behaviour (and the resulting reaction of the children to a
robot acting in a non-social way) represent an experimental baseline against which
future work can be compared.

@@

We introduce a novel dataset for the study of social cognition. The dataset
consists in dyadic free-play episodes, with children aged 4 to 8.

The dataset is built with machine learning applications in mind, and
particularly, applications to socio-cognitive robotics.

Finally, the social setting (two players facing each other) implicitly invites
social interaction: onlooker play, for instance, is unlikely to be observed as
the children are physically engaged with the game and the other participant
(they are sitting in front of game, close to each other). The three higher forms
of social play listed by Parten (parallel play, associative play and cooperative
play) are however possible with this setup.

>>>>

The children's faces are recorded using two short range Intel RealSense SR300
RGB-D cameras (0.2m to 1.2m) placed at the corners of the sandtray
(Fig.~\ref{fig|freeplay}) and tilted to face the children. The
cameras are rigidly mounted on custom 3D-printed brackets. This enables a
precise measurement of their 6D pose relative to the touchscreen (extrinsic
calibration).

@@

\newcommand{\tabitem}{~~\llap{\textbullet}~~}
    \begin{tabular}{@{}p{0.2\linewidth}p{0.8\linewidth}@{}}
\toprule
\bf Greetings                     & \tabitem explain the purpose of the study: showing robots how children play  \\
\emph{(about 5 min)}              & \tabitem briefly present a Nao robot: the robot stands up, gives a short
                                    message (\emph{"Hello, I'm Nao. Today, I'll be watching you while you
                                    play and soon I'll be able to play with you. Is that alright?"}), and
                                    sits down. The robot is then put aside and does not intervene
                                    for the remaining of the experiment \\
                                    %Condition B: "Hello, I'm Nao. Today I'll be playing with you. Exciting!")\\ 
                                  & \tabitem place children on cushions \\ 
                                  & \tabitem give them the yellow/purple sports
                                  bibs and make sure their hair is tied \\ 
                                  & \tabitem complete demographics on the tablet \\
                                  & \tabitem remind the children that they can withdraw at anytime \\ \midrule
\bf Visual focus task             & \emph{(unrelated visual task where children gaze at a moving target)}\\ 
\emph{(30 sec)}                   & \\ \midrule
\bf Tutorial                      & explain how to interact with the game, ensure the children are confident with the manipulation/drawing \\ 
\emph{(1-2 min)}                  & \\ \midrule
\bf Items placement game          & \emph{(unrelated task on spatial reasoning -- as this task uses the same graphical environment as the main free-play task, it helps however the children to familiarise themselves with the game environment)} \\
\emph{(5 to 10 min)}              &  \\ \midrule
\bf Freeplay task                 & \tabitem initial prompt: \emph{"Just to remind you, you can use the animals or draw. Whatever you
                                  like. If you run out of ideas, there's also an ideas box. For example, the first one is a
                                  zoo. You could draw a zoo or tell a story. When you get bored or don't want to play
                                  anymore, just let me know."} \\
                                  & \tabitem let children play \\
                                  & \tabitem once they wish to stop, stop recording \\ \midrule
\bf Debriefing                    &  \tabitem answer possible questions from the children \\
\emph{(about 2 min)}              & \tabitem give stickers as a thank you \\ \bottomrule
\end{tabular}

@@

The last part of the dataset consists in annotations of the children's social
behaviours. These behaviours are either automatically computed and coded
(mutual gaze, for instance), or are human-coded. The annotations are all
timestamped and integrated as an supplementary datastream in the dataset.

@@

The dataset includes two types of manual annotations: \emph{remarkable events},
annotated by the experimenter during the experiment as free text annotation, and
\emph{social behaviours} coded with the \emph{Social Communication Coding
System} (SCCS) proposed by Olswang~\etal\cite{olswang2006reliability}.
The SCCS consists in 6 mutually exclusive constructs characterising social
communication (Table~\ref{table|sccs}). These behaviours represent a typical
classification output that a network could be trained to recognise.

The SCCS coding is performed post-hoc with the help of a dedicated tool, able
to replay synchronously the main datastreams (Fig.~\ref{fig|analysis}) while
the human coder annotates the interaction.

@@

\begin{figure}[th!]
    \centering
    \includegraphics[width=0.8\linewidth]{analysis}
    \caption{Screenshot of our interaction annotation tool: the recorded interaction data
    is played back synchronously (faces and audio of the two children,
    interaction occurring on the interactive table, environment camera) while the human coder
    annotates the record timeline with social situations of interest.}
    \label{fig|analysis}
\end{figure}

@@

The dataset is freely available to any interested researcher\footnote{Note to
the reviewers: for the purpose of the review, an excerpt of the dataset is
available online: \url{https://freeplay-sandbox.github.io/}. A link to the
complete dataset will be made available with the final version of the article.}.
Due to ethical and data protection regulations, the dataset is however made
available in two forms: a public, Creative Commons licensed, version that does
not include any video material of the children (no video streams, audio
included); and a complete version that includes all video streams. This second
version is freely available as well, but interested researchers must first fill
a data protection form.

@@

During the acquisition campaign for the PInSoRo dataset, we have also recorded a
\emph{child-robot} interaction baseline. We use the exact same protocol
as described above, only with one child replaced by a Nao robot.

The robot is fully autonomous, and programmed to exhibit a \emph{non-social}
behaviour (its action policy is simply to repeatedly move interactive items to
pre-defined zones, entirely ignoring its child partner).  This behaviour (and
the resulting reactions of the children to a robot acting in a non-social way)
represents an experimental baseline against which future work on social
human-robot interaction can be compared.

This second dataset is public as well, and is made available to the interested
researchers under the same conditions as the child-child interaction dataset.

@@

In this article, we have introduced a novel dataset for the study of early
social cognition. The dataset consists in dyadic free-play episodes with
children aged 4 to 8. The interactions are scaffolded by a novel, playful task,
and a large range of social behaviours have been observed: pro-social behaviours
(for instance, helping behaviours, negotiations, natural turn-taking),
antagonistic behaviours (for instance, disrupting behaviours, refusal to
cooperate), assertive behaviours (dominant behaviours, manipulative behaviours)
and numerous episodes of off-topic actions and interactions.

For a robot to recognise such behaviours and situations would be of great
interest to the human-robot interaction community as it would effectively
increase the robot's situation awareness. This would in turn enable the robot to
respond appropriately to the complex social situations encountered in real-world
scenarios.

Our dataset is open, and built with machine learning applications in mind, and
particularly, applications to socio-cognitive robotics: we hope it will
effectively contribute to bridge the gap between machine learning and social
robotics, and support the research efforts of our community.

%Finally, the social setting (two players facing each other) implicitly invites
%social interaction: onlooker play, for instance, is unlikely to be observed as
%the children are physically engaged with the game and the other participant
%(they are sitting in front of game, close to each other). The three higher forms
%of social play listed by Parten (parallel play, associative play and cooperative
%play) are however possible with this setup.
